Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-01-29 draft.tex
linear optimization

\DeclareMathOperator{\SCORE}{Score}
\DeclareMathOperator{\PMR}{PMR}
\DeclareMathOperator{\MR}{MR}
\DeclareMathOperator{\MMR}{MMR}

@@

%Given a full profile: use linear programming to maximize regret
%Given a partial profile: use techniques of Lu and Boutilier (2011).
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
In the classical setting, the social choice rule is fixed beforehand; indeed many works analyze the properties of different rules (including axiomatic treatments) in order to justify the choice of specific social choice functions. 
Moreover, it is usually assumed that the preferences of the voters are completely known.

%We argue that it is possible that the committee wants to precise some preferences about the aggregation.
In this draft we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.
We note that previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.
%We consider that the committee wants to express preferences for some voting rules
In this draft we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret.

@@

We assume that there is a set $A$ of $m$ alternatives and $n$ agents (voters); each agent is associated to a preference order.
%The set of preference orders is called profile and it is denoted by $v$.
The preferences of the agents are supposed to be linear orders (connected, transitive, asymmetric relations) involving the alternatives;
$\pref_i$ denotes the ``real'' preference relation of agent $i$. 
The set $(\pref_1,\ldots,\pref_n)$ is known in the social choice literature as the {\em preference  profile}.
The profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_i(j)$ denotes the rank (position) of alternative $j$ in the preference order $\pref_i$. 
With a little abuse of notation, we will use the term profile to refer to either $\profile$ or to the preference relations, depending on the context.
Let $V$ be the set of possible preference profiles (the cartesian product of $n$ linear orders).

A social choice function $f : V \rightarrow 2^A$ associates a profile with a set of winners.
Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions; an alternative obtains a score that depends on the rank obtained in each of the preference orders:

\[ s(x; \profile, \w) = \sum_{i=1}^{n} w_{v_i(x)}. \]

where the vector $(w_1,\ldots,w_m)$ is called the scoring vector. We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.

\medskip
We want to reason about partial preference information.
A partial preference  is encoded by a partial order $\ppref_i$  of voter $i$;
we assume that preference information is truthful, i.e. $a \ppref_i b \implies a \pref_i b$.

@@

\section{Related works}

@@

\section{Minimax regret under partial profile and weight information}
In this draft, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.

The weights of a scoring rule can model different preferences for the committee; however in general it can be difficult to set the weights in an appropriate way.

The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the committee).

%The adversary can choose the instantiation of the weights and preferences of the agents so to maximize the loss.

We propose to use minimax regret to identify the alternative to declare as the approximate winner, extending the work of \cite{Lu2011} to the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.
The maximum regret is considered by assuming an adversary can choose both 1) to extend the partial profile into a complete profile 2) can instantiate the weights choosing among any feasible weight vector in $W \subseteq \mathcal{W}$.

\begin{align*}
\PMR(x,y; \pprofile, W) &= \max_{\w \in W} \max_{\profile \in C(p)} s(y; \profile,\w) - s(x; \profile,\w)\\
\MR(x; \pprofile, W) &= \max_{y \in A} \PMR(x,y; \pprofile, W) \\
\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
x^{*}(\pprofile,W) & \in \arg\min_{x \in A} \MR(x;\pprofile,W) 
\end{align*}

\begin{itemize}
 \item $\PMR(x,y;\pprofile,W)$ denotes the pairwise max regret of $x$ relative to $y$ given partial profile $\pprofile$ and the space of weights $W$, that is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights.
 \item Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$. It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $w$.
 \item Minimax regret $\MMR(\pprofile,W)$ is the minimum of max regret obtained when choosing $x^*$
\end{itemize}
By recommending the alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).

We want to design a questioning strategy to minimize the worst regret in the long run. A questioning strategy indicates, given a partial profile and a set of feasible weights, which question to ask next. A question is either a query to the voter $i$ about her preference relation $\succ_i$ or a query to the committee about the feasible weights.

In order to design this strategy we first evaluate how to compute the current regret.

\subsection{Computation of minimax regret}

In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \cite{Lu2011} so that we decompose the $\PMR$ into the contributions that is associated to each agent.
The settings is however more challenging due to the presence of uncertainty in the weights.

Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points $x$ obtains in the ranking $v_j$, that is the weight of the position $v_j(x)$.
Exploiting the decomposition of the score in terms of votes we can rewrite $\PMR$ as follows:
\begin{align*}
\PMR(x,y; \pprofile, W) &= \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] = \\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [s(y; v_j,\w) - s(x; v_j,\w)]=\\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}] \\
\end{align*}

Given our hypothesis, for all pairs of alternatives, there exists completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. That is, we can exhibit, for each voter $j$, a completion $v_j$ such that $\forall \w, \forall v'_j \in C(\ppref_j): [w_{v_j(y)} - w_{v_j(x)}] \geq [w_{v'_j(y)} - w_{v'_j(x)}]$.

@@

\section{Interactive Elicitation}
Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
While it is of course possible doing full elicitation of the weights and afterwards elicit the agents' preferences (or the other way around) we propose an interleaved approach.
In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
Indeed, it can be beneficial to interleave questions asked to the committee and questions asked to voters, depending on which is estimated to be more informative.

@@

{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agents depending on which is highest}

@@

\begin{itemize}
\item \textbf{Current solution strategy}: consider the solution of the minimax regret game, 
 $(x,y,w^{a},\profile^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.

@@

\item Non-interleaved regret method: comparison with a method based on minimax regret, but not interleaved.

@@

We evaluate the proposed method using the following simulated protocol.

@@

Test with different values of $m$ (number of alternatives) and $n$ (number of agents).

Test with different population sizes, different number of alternatives, etc.

@@

@@

\pagebreak
\appendix
\section{Minimax Computation under Convex Assumption \cite{Lu2011}}
The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights. Assume hereinafter the selected weights sequence $\w \in W$ to be convex. In order to compute the minimal max regret $\MMR(\pprofile)$ under partial profile $\pprofile$ we need to compute the pairwise max regret between all pairs of alternatives $(x,y)$, where $x$ is a proposed winner and $y$ is the ``adversary'' alternative. Indeed, the construction of $\PMR(x,y,\pprofile,\w)$ can be viewed as an adversary's attempt to maximize the regret of choosing $x$ instead of $y$. For doing this, he can choose a completion $\profile_i \in C(\pprofile_i)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the voter $i$ to $\PMR(x,y,\pprofile,\w)$. Let us now analyze how it could be done depending on the relation between alternatives $x$ and $y$ in $\pprofile_i$. 
\begin{itemize}
	\item $x \succ_i^\pprofile y$
	\newline If we know $x$ is preferred to $y$ and we choose $x$ as a winner, $\pprofile_i$ contribution to $\PMR(x,y,\pprofile,\w)$ must be negative. In this situation, our adversary can only try to minimize this advantage by minimizing the positional gap between the two alternatives. To achieve that, he can arbitrary place all the alternatives preferred to $x$ above $x$, together with all the ones with unknown relation to $x$. Moreover, he can place all the alternatives less preferred to $x$ and with unknown relation to $y$ below $y$. We can summarize it for each $q \in A$ as follows:
	\begin{align*}
	q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x \ & \Rightarrow \ \uparrow_x \\
	x \succ_i^\pprofile q \wedge ( q \ ?_i^\pprofile \ y \vee y \succ_i^\pprofile q) \ & \Rightarrow \ \downarrow_y \\
	x \succ_i^\pprofile q \succ_i^\pprofile y \ & \Rightarrow \ \text{in between} \\
	\end{align*}
	It is worth noting that when the relation between $q$ and $x$ is not known in the partial profile, the adversary takes advantage by placing $q$ above $x$ only under the assumption of convex weight sequences.
	\item $y \succ_i^\pprofile x$
	\newline If $y$ is preferred to $x$ the construction proceeds similarly to the previous case, but now the adversary takes advantage by maximizing the gap between $x$ and $y$ placing as much alternatives as he can between the two. We can summarize the procedure for each $q \in A$ as follows:
	\begin{align*}
	q \succ_i^\pprofile y \ & \Rightarrow \ \uparrow_y \\
	x \succ_i^\pprofile q \ & \Rightarrow \ \downarrow_x \\
	(y \succ_i^\pprofile q \vee y \ ?_i^\pprofile \ q) \wedge (q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x) \ & \Rightarrow \ \text{in between} \\
	\end{align*}
	\item $x \ ?_i^\pprofile \ y$
	\newline If the partial profile $\pprofile_i$ does not specify the relation between $x$ and $y$, the advantage is maximized by ordering $y$ over $x$ and maximizing the gap between them following the procedure for the case $y \succ_i^\pprofile x$.
\end{itemize}

@@

\subsection{Profile completion, again}
 {\bf \em TODO: still have to find out exactly how to do it}
 We introduce a set integer variables $I^i$, one for each position $i$.
 Let $U^j$ be, for the agents in $A^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in A^-$, are incomparable with $x$ and $y$.
 \[ \sum_{l=1}^n I^j_l w_l \]
 Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.

 Use linearization techniques to handle the multiplication...

\section{To discuss}
Let $\hat{v}_i$ be the linear order extending $p_i$ according to the above procedure (described in \cite{Lu2011}).

Then PMR can be written as follows:
\[ \PMR(x,y; \pprofile, W) = \max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]  + \sum_{j \in A^+, j \in A^?} [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \Big \} \]

\section{Even more fun}
We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.

Type of questions that we can ask to the chair:
bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).

>>>>

\DeclareMathOperator{\Regret}{Regret}
\DeclareMathOperator{\SCORE}{Score}
\DeclareMathOperator{\PMR}{PMR}
\DeclareMathOperator{\MR}{MR}
\DeclareMathOperator{\MMR}{MMR}

@@

%Given a full profile: use linear programming to maximize regret
%Given a partial profile: use techniques of Lu and Boutilier (2011).
\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
In the classical setting, the social choice rule is fixed beforehand; indeed many works analyze the properties of different rules (including axiomatic treatments) in order to justify the choice of specific social choice functions. 
Moreover, it is usually assumed that the preferences of the voters are known completely.

%We argue that it is possible that the committee wants to precise some preferences about the aggregation.
In this draft we depart from the classic view by considering that both preferences and the social choice rule can be only partially specified.
We note that previous works have considered either partial preferences or a partially specified aggregation, but we do not know of any work considering both sources of uncertainty at the same time.
%We consider that the committee wants to express preferences for some voting rules
In this draft we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret. 
\end{abstract}

\section{Introduction}

\begin{itemize}
\item General motivation: need to deal with partially specified preferences and as well partially specified voting rules
\item Focus on positional scoring rules
\item Robust decision criterion: minimax regret
\item Incremental elicitation of preferences can help mitigating the cognitive and communication costs
\item Novelty of the proposed method
\item Structure of the paper
\end{itemize}

Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
In many situations, such as in group recommender systems, the goal is to find a consensus choice.

In this paper we propose an interactive adaptive protocol for eliciting both the voters preferences and the voting rule.
At each step we need to decide whether we want to ask a question to the committee or to one of the agents (and to which agent in particular).
%We want to design a questioning strategy to minimize the worst regret in the long run. A questioning strategy indicates, given a partial profile and a set of feasible weights, which question to ask next. A question is either a query to the voter $i$ about her preference relation $\succ_i$ or a query to the committee about the feasible weights.

%The voting scheme selects the winner (a consensus option).
%Incremental elicitation 
% The paper is organized as follows.

\subsection{Related works}

@@

We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
The goal of the voters is to make a consensus choice, that is to select a ``winner'' given voter rankings.

%The set of preference orders is called profile and it is denoted by $v$.
The preferences of the agents are supposed to be linear orders (connected, transitive, asymmetric relations) involving the alternatives;
$\pref_i$ denotes the ``real'' preference relation of agent $i$. 
The set $(\pref_1,\ldots,\pref_n)$ is known in the social choice literature as the {\em preference  profile}.
The profile is equivalently represented by $\profile=(v_1,\ldots,v_n)$ where $v_i(j)$ denotes the rank (position) of alternative $j$ in the preference order $\pref_i$. 
With a little abuse of notation, we will use the term profile to refer to either $\profile$ or to the preference relations, depending on the context.
Let $V$ be the set of possible preference profiles (the cartesian product of $n$ linear orders).

A social choice function $f : V \rightarrow 2^A$ associates a profile with a set of winners.
Among the many possible social choice functions, we consider {\em positional scoring rules}, which attach weights to positions; an alternative obtains a score that depends on the rank obtained in each of the preference orders:
\begin{align}
s(x; \profile, \w) = \sum_{j=1}^{n} w_{v_j(x)}
= \sum_{i=1}^{m} \alpha_i w_i . \label{eq:srule}
\end{align}
where $\alpha_i$ is the number of times that alternative $x$ was ranked in the $i$-th position.
The vector $(w_1,\ldots,w_m)$ is called the scoring vector. We assume that the weights constitute a monotonic sequence: $w_{1} \geq w_{2} \geq \ldots \geq w_{m}$.

\medskip
In this work we want to reason about partial preference information.
A partial preference  is encoded by a partial order $\ppref_i$  of voter $i$;
we assume that preference information is truthful, i.e. $a \ppref_i b \implies a \pref_i b$.

@@

@@

\section{Minimax regret under partial profile and weight information}

%The regret-minimizing alternative may not be a possible winner for some voting rules.
The weights of a scoring rule can model different preferences of the committee. 
For instance, the weights can control the inclination to favour ``extreme'' alternatives (often at either the top or the bottom of the rankings) at the expenses of ``moderate'' alternatives (that are more consistently in the middle part of the rankings).

However in general it can be difficult to set the weights in an appropriate way.

In this paper, we consider a setting where both the voters' preferences and the preferences of the chair about the voting rule are incomplete.

\medskip
The quality of an alternative can be quantified by considering the maximum regret with respect to an adversary that can choose the instantiation of both a complete profile (extending the known preferences of the agents) and of the scoring vectors (associated to the preferences of the committee).

We propose to use the minimax regret as a decision criterion to determine a winner.
Minimax regret [ref] has been used for making decisions under utility uncertainty and for preference elicitation [ref].
Lu and Boutilier \cite{Lu2011} have adopted minimax regret ;

This paper extends the work of  to the simultaneous presence of uncertainty in the agents' preferences and uncertainty in the weights.

The maximum regret is considered by assuming an adversary can choose both 1) to extend the partial profile into a complete profile 2) can instantiate the weights choosing among any feasible weight vector in $W \subseteq \mathcal{W}$.

We formalize the notion of minimax regret in multiple steps.
First of all, $\Regret(x, \profile, \w)$ is the loss or ``actual'' regret  of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
\[\Regret(x, \profile, \w) = \max_{y} s(y; \profile,\w) - s(x; \profile, \w).\]

The pairwise max regret of $x$ relative to $y$ given partial profile $\pprofile$ and the space of weights $W$
$\PMR(x,y;\pprofile,W)$ is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
\begin{align}
\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(p)} s(y; \profile,\w) - s(x; \profile,\w).
\end{align}

Max regret $\MR(x;\pprofile,W)$ is the worst-case loss of $x$. It is the loss occurred by an adversarial selection of a complete profile $\profile$ extending $\pprofile$ and a selection of $\w \in W$ to maximize the loss between $x$ and the true winner under $\profile$ and $w$.
\begin{align}
\MR(x; \pprofile, W) & = \max_{y \in A} \PMR(x,y; \pprofile, W)\\
& = \max_{\w \in W} \max_{\profile \in C(p)} \Regret(x, \profile, \w).
\end{align}

Finally,  $\MMR(\pprofile,W)$ is the value of minimax regret under $\pprofile$ and $W$, obtained when recommending the minimax optimal alternative $x^*$:
\begin{align*}
\MMR(\pprofile,W) & = \min_{x \in A} \MR(x;\pprofile,W) \\
x^{*}(\pprofile,W) & \in \arg\min_{x \in A} \MR(x;\pprofile,W) 
\end{align*}
By recommending the alternative associated with minimax regret, we can provide a recommendation that gives worst-case guarantees, giving some robustness in face of uncertainty (due to both not knowing the agents' preferences and the weights used in the aggregation).

% Add some general remarks about using minimax regret

\subsection{Computation of minimax regret}
In order to compute pairwise maximum regret and therefore minimax regret, we adapt the reasoning from \cite{Lu2011} so that we decompose the $\PMR$ into the contributions that is associated to each agent.
The settings is however more challenging due to the presence of uncertainty in the weights.

A scoring rule associates each alternative to a score that is given by the sum of points obtained for each voter.

Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}), that is the weight of position $v_j(x)$.
Obviously we have 
\[ s(x; \profile, \w) = \sum_{j=1}^n s(x; v_j,\w). \]

We now  exploit the decomposition of the score in terms of votes.
The actual regret of choosing $x$ instead of $y$ can be written as:
\[
s(y; \profile,\w) - s(x; \profile, \w) = [\sum_{j=1}^n s(y; v_j,\w) - s(x; v_j,\w)]
\]
and  can rewrite $\PMR$ as follows:
\begin{align*}
\PMR(x,y; \pprofile, W) &= \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] = \\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [s(y; v_j,\w) - s(x; v_j,\w)]=\\
&=  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}] \\
\end{align*}
Given our hypothesis, for all pairs of alternatives, there exists completions of the partial preferences $\ppref$ that maximize the PMR and that do not depend on the weights. 
That is, we can exhibit, for each voter $j$, a completion $v_j$ such that $\forall \w, \forall v'_j \in C(\ppref_j): [w_{v_j(y)} - w_{v_j(x)}] \geq [w_{v'_j(y)} - w_{v'_j(x)}]$.

@@

\subsection{Linear program under the convex assumption}

By solving a sequence of pairwise max regret computation is possible to determine the minimax regret solution.
Each PMR is computed using a linear program.
The decision variables correspond to the weights attached to the different positions.
Constraints are on the feasible parameters (the ``weights'' of the scoring rules); contraints represent the preferences of the chair about the scoring rule.

Let $\hat{v}$ be the compute profile computed according to the above procedure, and  $\hat{v}_j$ the $j$-th element (the linear order extending the partial order $p_j$ of the $j$-th voter).
The PMR can be written as:
\[ \PMR(x,y) = \sum_{j=1}^n w_{\hat{v}_i(y)} - w_{\hat{v}_i(x)} 
= \sum_{i=1}^m \alpha_i w_i \]
where the coefficient $\alpha_i$ is the number of times $y$ is in the $i-th$ position minus the number of times $x$ is the in the $i$-th position in the rankings of the completed profile $\hat{v}$:
\[ \alpha_{i} = \sum_{j=1}^{n}  I[\hat{v}_{j}(y)=i] - I[\hat{v}_{j}(x)=i]\]
where $I$ is the indicator function.
The linear program is then the following:
\begin{align}
\max & \sum_{i=1}^m \alpha_i w_{i}\\
\text{ s.t. } & w \in W
\end{align}

\subsection{Minimax regret without the convex assumption}

\begin{itemize}
 	\item Mixed integer program to solve minimax regret without the convexity
 	\item Approximations ?
\end{itemize}

Let $\hat{v}_i$ be the linear order extending $p_i$ according to the above procedure (described in \cite{Lu2011}).
Then PMR can be written as follows:
\[ \PMR(x,y; \pprofile, W) = \max_{\w \in W} \Big \{ \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]  + \sum_{j \in A^+, j \in A^?} [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \Big \} \]

We compute pairwise maximum regret by considering binary variables to represent optimization choices related to where to position the alternatives.
We also have numerical variables to represent the weights of the scoring rule.

Since the objective is to maximize pairwise regret

 The objective function can be written as:
 \[ \max \sum_{l=1}^n I^j_l w_l -  I^j_l w_l \]

 We replace the multiplicative terms by new variables..
\[ V_{l}^{j} \sim I^j_l w_l  \]

To impose the desired behavior:
\begin{align*} 
V_{l}^{j} \leq I^j \\
V_{l}^{j} \leq w_l
\end{align*}
The expression $I^j_l w_l$ evaluates to $w_l$ if $I^j_l = 1$, and to $0$ otherwise.

We write $w \in W$ as a shourtcut to represent the constraints that the weights are chosen to be in the feasible set.
%Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.

\begin{align}
\max & \sum_{l=1}^m  V_{l}^{j,+} - V_{l}^{j,-}\\
\text{ s.t. } & \\
& V_{l}^{j} \leq I^j \\
& V_{l}^{j} \leq w_l \\
& V_{l}^{j} \leq I^j \\
& V_{l}^{j} \leq w_l 
\end{align}

\section{Interactive Elicitation}

\begin{itemize}
	\item Minimax regret can be used to guide the elicitation process
	\item As termination condition of elicitation, we can check whether minimax regret is lower than a threshold. If optimality is derived, we can perform elicitation until minimax regret drops to zero.
	\item At each step, the system need to decide whether to ask a question to one of the agents or ask a question to the chair about the voting rule
	\item Type of questions that we can ask to the chair:
	bound queries (Is this alternative among your top-k most preferred items?), comparison queries (do you prefer alternative x or alternative y?).
\end{itemize}

Starting from some initial partial knowledge, our goal is to learn both the scoring rule function and the agents' preferences.
While it is of course possible doing full elicitation of the weights and afterwards elicit the agents' preferences (or the other way around) we propose an interleaved approach.
In our interactive  protocol for simultaneously eliciting the preferences of the chair about the voting rule and the voters' preferences about the alternatives.
Indeed, it can be beneficial to interleave questions asked to the committee and questions asked to voters, depending on which is estimated to be more informative.

@@

%{\em Some ideas: decompose the regret into two components, one due to $\w$ and one due to $\pprofile$, and ask a question to the chair / or to one of the agents depending on which is highest}

@@

\begin{itemize}
\item {\em Current solution strategy}: consider the solution of the minimax regret game, 
 $(x,y,\w^{a},\profile^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $\w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.

Ask a question to compare $x$ with $y$ to an agent.

@@

\item Two phase method.
Ask a predefined (non adaptive) sequence of questions in order to learn the weights $w$ of the scoring rule).
Then use minimax regret as in Lu and Boutilier.

%\item Non-interleaved regret method: comparison with a method based on minimax regret, but not interleaved.

@@

% We can stop elicitation when minimax regret is sufficiently small.
We evaluate the proposed method using the following simulated protocol.

We test the elicitation protocols in randomly generated datasets and real datasets (sushi and iris).

@@

Test with different values of $m$ (number of alternatives) and $n$ (number of agents); test with different population sizes, different number of alternatives, etc.

@@

% Conclusions
% summary of contribution, more comments, future works.

@@

\pagebreak
\appendix
\section{Minimax Computation under Convex Assumption}

Refer to \cite{Lu2011}
The goal is to choose as a winner the alternative $x^*$ whose worst case loss is minimal under all possible realizations of the full profile and all possible choices of weights. 
Assume hereinafter the selected weights sequence $\w \in W$ to be convex. 
In order to compute the minimal max regret $\MMR(\pprofile)$ under partial profile $\pprofile$ we need to compute the pairwise max regret between all pairs of alternatives $(x,y)$, where $x$ is a proposed winner and $y$ is the ``adversary'' alternative. Indeed, the construction of $\PMR(x,y,\pprofile,\w)$ can be viewed as an adversary's attempt to maximize the regret of choosing $x$ instead of $y$. 
For doing this, he can choose a completion $\profile_i \in C(\pprofile_i)$ of the partial profile and a (feasible) scoring vector $\w$ that maximize the contribution of the voter $i$ to $\PMR(x,y,\pprofile,\w)$. Let us now analyze how it could be done depending on the relation between alternatives $x$ and $y$ in $\pprofile_i$. 
\begin{itemize}
	\item $x \succ_i^\pprofile y$
	\newline If we know $x$ is preferred to $y$ and we choose $x$ as a winner, $\pprofile_i$ contribution to $\PMR(x,y,\pprofile,\w)$ must be negative. In this situation, our adversary can only try to minimize this advantage by minimizing the positional gap between the two alternatives. To achieve that, he can arbitrary place all the alternatives preferred to $x$ above $x$, together with all the ones with unknown relation to $x$. Moreover, he can place all the alternatives less preferred to $x$ and with unknown relation to $y$ below $y$. We can summarize it for each $q \in A$ as follows:
	\begin{align*}
	q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x \ & \Rightarrow \ \uparrow_x \\
	x \succ_i^\pprofile q \wedge ( q \ ?_i^\pprofile \ y \vee y \succ_i^\pprofile q) \ & \Rightarrow \ \downarrow_y \\
	x \succ_i^\pprofile q \succ_i^\pprofile y \ & \Rightarrow \ \text{in between} \\
	\end{align*}
	It is worth noting that when the relation between $q$ and $x$ is not known in the partial profile, the adversary takes advantage by placing $q$ above $x$ only under the assumption of convex weight sequences.
	\item $y \succ_i^\pprofile x$
	\newline If $y$ is preferred to $x$ the construction proceeds similarly to the previous case, but now the adversary takes advantage by maximizing the gap between $x$ and $y$ placing as much alternatives as he can between the two. We can summarize the procedure for each $q \in A$ as follows:
	\begin{align*}
	q \succ_i^\pprofile y \ & \Rightarrow \ \uparrow_y \\
	x \succ_i^\pprofile q \ & \Rightarrow \ \downarrow_x \\
	(y \succ_i^\pprofile q \vee y \ ?_i^\pprofile \ q) \wedge (q \succ_i^\pprofile x \vee q \ ?_i^\pprofile \ x) \ & \Rightarrow \ \text{in between} \\
	\end{align*}
	\item $x \ ?_i^\pprofile \ y$
	\newline If the partial profile $\pprofile_i$ does not specify the relation between $x$ and $y$, the advantage is maximized by ordering $y$ over $x$ and maximizing the gap between them following the procedure for the case $y \succ_i^\pprofile x$.
\end{itemize}

@@

\subsection{Profile completion, again}
 %{\bf \em TODO: still have to find out exactly how to do it}

 We introduce a set integer variables $I^i$, one for each position $i$.
 Let $U^j$ be, for the agents in $A^-$, the alternatives that, in the partial order $\succ^p_j$ of some agent $j \in A^-$, are incomparable with $x$ and $y$.
 \[ \sum_{l=1}^n I^j_l w_l \]
 Variable $I^j$ associated with the constraint $0 \leq I \leq |U^j|$.

 We provide the following MIP (mixed integer linear program).

% Use linearization techniques to handle the multiplications...

%\section{Even more fun}
%We can consider different types of questions: asking to compare a pair of alternatives, asking about top-k alternatives.
%
